### 2022-02-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b4399a5a1602cc5d454dbfc0b5cabcdfa5c29ced 🚀

>>>>

\textbf{Conflict of interest:} The authors have no conflict interests to
disclose

\textbf{Authors' contributions:} TS, and TP conceived the ideas
discussed in the manuscript. All authors contributed to writing and
editing the manuscript.

\textbf{Data availability:} There is no data associated with this
manuscript.
